---
title: "Linear regression and fixed effects"
author: "Christian Olms<git@christianolms.de>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{knitr,xtable,PaneldatenUeb}

---

#Dataset
This packages contains the Fatalities dataset. The following code produces an overview of the columns.
```{r, warning=FALSE, message=FALSE}
library(ContextVariableCreation)
library(data.table)
library(foreach)
library(ggplot2)
data("Fatalities", package = "AER")
#summary(Fatalities)
```
The dataset contains 7 rows for every of the 48 states for the years 1982 to 1988.
First, add traffic death per 1000 miles.

#Ordinary least square model
```{r}
Fatalities$frate <- with(Fatalities, fatal/pop * 10000)
```
Then create a ordinary least square model.

```{r}
mod_sig = frate~ beertax
df_reg = create_context_variables_for_panel(Fatalities, group_variable = "state",time_dep_variables = c("beertax"))
m1 = glm(formula = mod_sig, data = df_reg, family = gaussian())
summary(m1)
source("../R/plots.R")
print(plot_residuals(residuals = m1$residuals, target = Fatalities$frate))
```


##Effect of countries

```{r}
ggplot(aes(x=frate,y=beertax, color=state), data = Fatalities)+geom_point()
```

Interpretation with beertax in us dollar:
if beer tax  get higher, the slope

Linear regression with fixed effects
```{r}
m2 = glm(formula = frate~ beertax + beertax_cv, data = df_reg, family = gaussian())
summary(m2)
print(plot_residuals(residuals = m2$residuals, target = Fatalities$frate))
```

##Model comparision


```{r}
anova(m1,m2)
```
